---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covid19france

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/Covid19R/covid19france.svg?branch=master)](https://travis-ci.org/Covid19R/covid19france)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/covid19france)](https://CRAN.R-project.org/package=covid19france)
<!-- badges: end -->

This package contains summary datasets of COVID-19 cases in France, averaged from the [opencovid19-fr](https://github.com/opencovid19-fr/data) data, available on GitHub. (README in English available [here](https://github.com/opencovid19-fr/data/blob/master/README.en.md).)

## Installation

``` r
# install.packages("devtools")
devtools::install_github("Covid19R/covid19france")
```
## Data

```{r example}
library(covid19france)
```

The two package datasets are available once the package is attached.

```{r}
tibble::as_tibble(france_country)
```

```{r}
tibble::as_tibble(france_regional)
```

If you want to update the datasets, run `refresh`.

```{r, warning=FALSE}
refresh()
```


## Contributing

Please submit [issues](https://github.com/Covid19R/covid19france/issues) and [pull requests](https://github.com/Covid19R/covid19france/pulls) with any package improvements!

Please note that the 'covid19france' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
