---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```

# covid19france

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/Covid19R/covid19france.svg?branch=master)](https://travis-ci.org/Covid19R/covid19france)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/covid19france)](https://CRAN.R-project.org/package=covid19france)
<!-- badges: end -->

This package provides per-day data on COVID-19 cases in France.

The data is an average over all of the sources provided by [opencovid19-fr](https://github.com/opencovid19-fr/data). (README in English available [here](https://github.com/opencovid19-fr/data/blob/master/README.en.md).)

## Installation

``` r
# install.packages("devtools")
devtools::install_github("Covid19R/covid19france")
```
## Data

```{r example}
library(covid19france)
```

Get the full dataset:

```{r}
(france <- refresh_covid19france())
```

To switch to a wider format, you can use `tidyr`:

```{r}
france %>% 
  tidyr::pivot_wider(
    names_from = "data_type"
  ) %>% 
  dplyr::select(
    1, 6:ncol(.), everything()
  )
```

For more info on the dataset:

```{r}
get_info_covid19france()
```

## Contributing

Please submit [issues](https://github.com/Covid19R/covid19france/issues) and [pull requests](https://github.com/Covid19R/covid19france/pulls) with any package improvements!

Please note that the 'covid19france' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
